R Notebook

### 2023-10-23 Subspace estimates.rmd
Add library connections

---
title: "R Notebook"
output: html_document
---
```{r}
N <- 10
M <- c(16, 16)
R <- length(M)
mu <- matrix(c(rep(1, R), rep(-0.5, R)), ncol = 2)
d <- ncol(mu)
s <- matrix(rep(40, R * N), ncol = N, byrow = TRUE)

>>>>

---
title: "R Notebook"
output: html_document
---
```{r}
library(purrr)
library(rTensor)

N <- 10
M <- c(16, 16)
# M <- rep(2, 8)
R <- length(M)
mu <- matrix(c(rep(1, R), rep(-0.5, R)), ncol = 2)
d <- ncol(mu)
s <- matrix(rep(40, R * N), ncol = N, byrow = TRUE)
